RMD Report Template

### 2025-01-29 reports/rmd-report-template.Rmd
Rmd report updated / template added.
Rmd report template fixed.

---
title: "Capstone Movielens Report"
author: "Azamat Kurbanaev"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

>>>>

---
title: "RMD Report Template"
author: "John Doe"
date: "`r Sys.Date()`"
output:
  html_document: 
    fig_caption: true
  pdf_document: 
    df_print: paged
    toc: true
    fig_caption: true
    keep_tex: true
---
